High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-05-01 notebooks/mnist.qmd
bleh

```{julia}
# Define generator:
revise_generator = REVISEGenerator(
  opt = opt,
  λ=0.1
)
# Generate recourse:
counterfactual_data.generative_model = vae # assign generative model
ce_strong = generate_counterfactual(
    x_factual, target, counterfactual_data, M, revise_generator; 
    decision_threshold=γ, max_iter=T,
    initialization=:identity,
    converge_when=:generator_conditions,
)
counterfactual_data_weak = deepcopy(counterfactual_data)
counterfactual_data_weak.generative_model = vae_weak
ce_weak = generate_counterfactual(
    x_factual, target, counterfactual_data_weak, M, revise_generator;
    decision_threshold=γ, max_iter=T,
    initialization=:identity,
    converge_when=:generator_conditions,
)
```

>>>>

```{julia}
# Define generator:
revise_generator = REVISEGenerator(
  opt = opt,
  λ=0.0
)
# Generate recourse:
counterfactual_data.generative_model = vae # assign generative model
ce_strong = generate_counterfactual(
    x_factual, target, counterfactual_data, M, revise_generator; 
    decision_threshold=γ, max_iter=T,
    initialization=:identity,
    converge_when=:generator_conditions,
)
counterfactual_data_weak = deepcopy(counterfactual_data)
counterfactual_data_weak.generative_model = vae_weak
ce_weak = generate_counterfactual(
    x_factual, target, counterfactual_data_weak, M, revise_generator;
    decision_threshold=γ, max_iter=T,
    initialization=:identity,
    converge_when=:generator_conditions,
)
```
